Exact asymptotic expressions for local clustering in hyperbolic random graphs

### 2018-10-24 introduction.tex
Added simulation section.

\subsection{Simulations}\label{ssec:simulations}

>>>>

\subsection{Simulations}\label{ssec:simulations}
The simulations of this section (see Figures \ref{fig:c2allnu}, \ref{fig:c4allnu} and \ref{fig:ckvariable}) confirm the formulas from the result section. The simulations were obtained by generating the hyperbolic random graph for a given choice of the parameters and number of repetitions and then taking the average over all simulation instances.
\begin{figure}
    \centering
    \includegraphics[scale=0.6]{figures/sim0123c2nualln1000rep20.pdf}
    %\includegraphics[scale=0.5]{figures/sim0128c4nualln10000rep20.pdf}
    \caption{Simulation of $c_{\mathbb{H},n}(k_n)$ for $k_n= 2$, for $\alpha$ varying from $0.5$ to $5$ on the horizontal axis and for $\nu=\frac{1}{2}$ (blue), $\nu=1$ (purple), $\nu=2$ (green); simulations (red dots) with $n=1000$ and 20 repetitions.}
    \label{fig:c2allnu}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[scale=0.6]{figures/sim0128c4nualln10000rep20.pdf}
    \caption{Simulation of $c_{\mathbb{H},n}(k_n)$ for $k_n= 4$, for $\alpha$ varying from $0.5$ to $5$ on the horizontal axis and for $\nu=\frac{1}{2}$ (blue), $\nu=1$ (purple), $\nu=2$ (green); simulations (red dots) with $n=10 000$ and 20 repetitions.}
    \label{fig:c4allnu}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[scale=0.6]{figures/sim1024ck225n10000a0609nu2rep20.pdf}
    \caption{Simulation of $c_{\mathbb{H},n}(k_n)$ for $k_n$ varying from 2 to 26 on the horizontal axis, for $\nu=2$ and $\alpha=0.6$ (green) and $\alpha=0.9$ (blue); simulations (red dots) with $n=10 000$ and 20 repetitions.}
    \label{fig:ckvariable}
\end{figure}
